Predicting Fatalities in Toronto Car Crashes: Analyzing the Impact of Time, Vehicle Type, and Other Collision Determinants from 2015 to 2024

### 2024-12-04 paper/paper.qmd
Added subtitle

---
title: "Predicting Fatalities in Toronto Car Crashes: Analyzing the Impact of Time, Vehicle Type, and Other Collision Determinants"
author: 
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/Kanghyunroe/traffic_collisions/tree/main](https://github.com/Kanghyunroe/traffic_collisions/tree/main)."
date: today
date-format: long
abstract: "This study aims to predict the likelihood of fatality in motor vehicle collisions (MVCs) in Toronto from 2014 to 2023, using data on crash time, vehicle type, and collision characteristics. By analyzing the interaction between hour of the day and vehicle types, including motorcycles and pedestrians, the model identifies key elements contributing to fatal outcomes. Results indicate that late-afternoon to evening hours, particularly between 5 PM and 11 PM, show a higher likelihood of fatalities, with motorcycles and pedestrians significantly increasing fatality risk. The model achieved a high predictive accuracy, demonstrating its potential in informing safety policies and interventions in Toronto."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Predicting Fatalities in Toronto Car Crashes: Analyzing the Impact of Time, Vehicle Type, and Other Collision Determinants from 2015 to 2024"
subtitle: "Vehicle Accidents Involving Motorcyclists and Pedestrians in the Evening Significantly Increases Fatality Risk"
author: 
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/Kanghyunroe/traffic_collisions/tree/main](https://github.com/Kanghyunroe/traffic_collisions/tree/main)."
date: today
date-format: long
abstract: "This study aims to predict the likelihood of fatality in motor vehicle collisions (MVCs) in Toronto from 2014 to 2023, using data on crash time, vehicle type, and collision characteristics. By analyzing the interaction between hour of the day and vehicle types, including motorcycles and pedestrians, the model identifies key elements contributing to fatal outcomes. Results indicate that late-afternoon to evening hours, particularly between 5 PM and 11 PM, show a higher likelihood of fatalities, with motorcycles and pedestrians significantly increasing fatality risk. The model achieved a high predictive accuracy, demonstrating its potential in informing safety policies and interventions in Toronto."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
